On the Synchronization of Computational RFIDs

### 2018-05-13 TMC-2017-11-0695-main.tex
Section 1.2 of the paper revised

\subsection{Differences From Battery-Powered WSNs }
\label{sec:Motivation}
\add{The EPC Gen2 uses slotted Aloha protocol that performs a form of synchronization between the reader and the tags: by adjusting clock offset differences and introducing guard times, tags are ensured to communicate at the allocated slot boundaries. However, this method does not compensate for clock drifts and output a synchronized clock value that can be accessed by the tags to timestamp (and make inference about) the collected information, e.g. from the sensors attached to tags. In consequence, applications requiring time notion cannot be enabled, since a clock should be maintained at each tag---making synchronization service mandatory. However, the characteristics of CRFID systems expose fundamentally different challenges than battery-powered sensor networks to implement the synchronization service. The reason is mainly twofold:}

>>>>

\subsection{Differences From Battery-Powered WSNs }
\label{sec:Motivation}

\add{The EPC Gen2 protocol uses slotted Aloha that performs a form of synchronization between the reader and the tags: by adjusting clock offset differences and introducing guard times, tags are ensured to communicate at the allocated slot boundaries. However, this method does not compensate for clock drifts and output a synchronized clock value that can be accessed by the tags to timestamp (and make inference about) the collected information, e.g. from the sensors attached to tags. In consequence, applications requiring time notion cannot be enabled, since a clock should be maintained at each tag---making synchronization service mandatory. However, the characteristics of CRFID systems expose fundamentally different challenges than battery-powered sensor networks to implement the synchronization service. The reason is mainly twofold:}
